---
title: Mapping cultural ecosystem services using social media tools – case study areas
  based across Europe
author: "Sandra Chiamaka Ikeh"
date: "18/07/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
  always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

### Load the packages

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(rtweet)
library(ggplot2)
library(dplyr)
library(imager)
library(ggthemes)
library(readr)
library(jsonlite)
library(tidytext)
library(wordcloud)
library(wordcloud2)
library(tidyr)#Spread, separate, unite, text mining (also included in the tidyverse package)
library(dplyr) #Data manipulation (also included in the tidyverse package)
library(tidytext) #Text mining
library(widyr) #Use for pairwise correlation

#Visualizations!
library(ggplot2) #Visualizations (also included in the tidyverse package)
library(ggrepel) #`geom_label_repel`
library(gridExtra) #`grid.arrange()` for multi-graphs
library(knitr) #Create nicely formatted output tables
library(kableExtra) #Create nicely formatted output tables
library(formattable) #For the color_tile function
library(circlize) #Visualizations - chord diagram
library(memery) #Memes - images with plots
library(magick) #Memes - images with plots (image_read)
library(yarrr)  #Pirate plot
library(radarchart) #Visualizations
library(igraph) #ngram network diagrams
library(ggraph) #ngram network diagrams
library(ggmap)
library(mapproj)


```

###Access to Twitter data, using the following keys and tokens.

```{r echo=FALSE, warning=FALSE, message=FALSE}
  oauth_consumer_key="xvz1evFS4wEEPTGEFPHBog"
  oauth_nonce="kYjzVBB8Y0ZFabxSWbWovY3uYSQ2pTgmZeNu2VS4cg" 
  oauth_signature="tnnArxj06cWHq44gCs1OSKk%2FjLY%3D" 
  oauth_signature_method="HMAC-SHA1"
  oauth_timestamp="1318622958"
  oauth_token="370773112-GmHxMAgYyLbNEtIKZeRNFsMKPR9EyMZeS9weJAEb"
  oauth_version="1.0"
```

#plot world globe

```{r}


#twitter_search_global <- Map(  # Map applies search_tweets to each element: "euenvironment", "eubiodiversity",
twitter_search_global <- Map(  # Map applies search_tweets to each element: "euenvironment", "eubiodiversity","euecosystem"
  "search_tweets",
  c ("euenvironment", "eubiodiversity" , "eu ecosystem"),
  lang = "en",
  include_rts = FALSE,
  n = 2000
)

#save(twitter_search_global2,file="twitter_search_global4.Rdata")
#save(file="twitter_search_global3.json")

#twitter_search_globalll <- fromJSON("twitter_search_global3.json")

twitter_search_global %>% toJSON() %>% write_lines("twitter_search_global4.json")
#
#
# Read in the data

#twitter_search_globalA <- stream_in(file("twitter_search_global4.json"))
#

plot_global <- do_call_rbind(twitter_search_global) %>% as.data.frame()





#plot_global <- (twitter_search_global2b) %>% as.data.frame()

plot_global <- lat_lng(plot_global) 


#create new data frame with just the tweet texts, usernames and location data
plot_global_s <- data.frame(date_time = plot_global$created_at,
                         username = plot_global$screen_name,
                         tweet_text = plot_global$text,
                         long = plot_global$lng,
                        lat = plot_global$lat)

# create basemap of the globe
# the theme_map() function cleans up the look of your map.

world_basemap <- ggplot() +
  borders("world", colour = "black", fill = "lightgrey") +
  theme_map()
world_basemap

#head(plot_global_s)
#plot_global_s
#
# remove na values
plot_global_locations <- plot_global_s %>%
 na.omit()

#plot_global_locations
#head(plot_global_locations)
#
#
# Plot the data modifying the basemap of the globe with ggplot2 features
#
world_basemap +
  geom_point(data = plot_global_locations, aes(x = long, y = lat),
             colour = 'darkred', alpha = .5) +
  labs(title = "Locations of tweets")

### Improve the plot to deal with overlapping points
# 
# round latitude and longitude and group close tweets
plot_global_locations_grp <- plot_global_locations %>%
  mutate(long_round = round(long, 2),
         lat_round = round(lat, 2)) %>%
  group_by(long_round, lat_round) %>%
  summarise(total_count = n()) %>%
  ungroup() %>%
  mutate(total_count = factor(total_count))
plot_global_locations_grp

# Plot tweet data on flood, earthquake, tsunami, grouping close tweets and 
# using larger points to show higer frequency
grouped_tweet_map <- world_basemap + 
  geom_point(data = plot_global_locations_grp,
            aes(long_round, lat_round, size = total_count),
            color = "purple", alpha = .5) + 
  coord_fixed() +
  labs(title = "Twitter Activity and locations of tweets on flood, earthquake, tsunami",
       size = "Number of Tweets")
grouped_tweet_map

```

# Now let's focus on search word Eu Environment

# Find the popular words from the tweets 

```{r}
twitter_search_global_eu_environment <- twitter_search_global$euenvironment
twitter_search_global_eu_environment

head(twitter_search_global_eu_environment$text)

# Frist, remove http elements manually
twitter_search_global_eu_environment$stripped_text <- gsub("http.*","",  twitter_search_global_eu_environment$text)
twitter_search_global_eu_environment$stripped_text <- gsub("https.*","", twitter_search_global_eu_environment$stripped_text)
head(twitter_search_global_eu_environment$stripped_text)

# Let's remove punctuation, convert to lowercase, add id for each tweet:
twitter_search_global_eu_environment_clean <- twitter_search_global_eu_environment %>%
  select(stripped_text, text) %>% 
  mutate(tweetnumber = row_number()) %>% # create new variable denoting the tweet number
  unnest_tokens(word, stripped_text)

head(twitter_search_global_eu_environment_clean)

# Now you can plot your data. 
# plot the top 10 words -- notice any issues?
twitter_search_global_eu_environment_clean %>%
  count(word, sort = TRUE) %>% # count of number of occurencies of each word and sort according to count
  head(10) %>% # extract top 10 words
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "pink", color = "red") +
  coord_flip() +
  labs(x = "Unique Words",
       y = "Frequency",
       title = "Count of unique words found in tweets with #climatechange") + 
  theme(axis.text = element_text(size = 16, color = "black"), 
        axis.title = element_text(size = 16, color = "black"),
        title = element_text(size = 18))

# load list of stop words - from the tidytext package
data("stop_words")
#
# view first 6 words
#head(stop_words)
# the lexicon is the source of the stop word.
#
#nrow(twitter_search_global_eu_environment_clean)
#

# remove stop words from your list of words
eu_environment_cleaned_tweet_words <- twitter_search_global_eu_environment_clean %>%
  anti_join(stop_words) # return all rows from climate_tweets_clean where there are not matching values in stop_words
#
# there should be fewer words now
nrow(eu_environment_cleaned_tweet_words)

eu_environment_cleaned_tweet_words %>%
  count(word, sort = TRUE) %>%
  head(10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "pink", color = "red") +
  coord_flip() +
  labs(x = "Unique Words",
       y = "Frequency",
       title = "Top 10 most popular words found in tweets with #climatechange") + 
  theme(axis.text = element_text(size = 14, color = "black"), 
        axis.title = element_text(size = 14, color = "black"),
        title = element_text(size = 16))

# Define our own stopwords that we don't want to include 
eu_environment_words <- data.frame(word = c("euenvironment", "eu", "environment" , "europe"))

# remove our own stopwords from the list of words too
eu_environment_cleaned_tweet_words_2 <- eu_environment_cleaned_tweet_words %>%
  anti_join(eu_environment_words) 
#
# there should be fewer words now
nrow(eu_environment_cleaned_tweet_words_2)

# plot the top 10 most popular words found in tweets with #climatechange
eu_environment_cleaned_tweet_words_2 %>%
  count(word, sort = TRUE) %>%
  head(10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "pink", color = "red") +
  coord_flip() +
  labs(x = "Unique Words",
       y = "Frequency",
       title = "Top 10 most popular words found in tweets with #climatechange") + 
  theme(axis.text = element_text(size = 14, color = "black"), 
        axis.title = element_text(size = 14, color = "black"),
        title = element_text(size = 16))


```

### plot Wordclouds for eu environment 

```{r}
head(eu_environment_cleaned_tweet_words_2)

# the count of each word / the total count
#
eu_environment_cleaned_tweet_words_3 <- eu_environment_cleaned_tweet_words_2 %>%
  count(word, sort = TRUE) %>% 
  mutate(freq = n / sum(n))
head(eu_environment_cleaned_tweet_words_3)

# Read the help file of wordcloud so that you can see what the arguments do
#
with(eu_environment_cleaned_tweet_words_3, 
     wordcloud(word, freq, 
               min.freq = 1, 
               max.words = 50,
               random.order = FALSE, 
               colors = brewer.pal(8, "Dark2"), 
               scale = c(4.5, 0.1)))

title(main = "Wordcloud for Tweets containing #euenvironment", 
      cex.main = 2) # Controls the size of the title

display.brewer.all()

eu_environment_cleaned_tweet_words_4 <- eu_environment_cleaned_tweet_words_3 %>% select(word, freq)
#
# Produce wordcloud
#
wordcloud2(eu_environment_cleaned_tweet_words_4)


```

#positive abd negative words

```{r}
# Join sentiment classification to the tweet words
eu_environment_bing_word_counts <- eu_environment_cleaned_tweet_words_2 %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  mutate(word = reorder(word, n)) 
head(eu_environment_bing_word_counts)
#
#
# Finally, plot top words, grouped by positive vs. negative sentiment. 
# it could be interesting to plot sentiment over time to see how sentiment changed over time.
#
eu_environment_bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(title = "Most common Positive and Negative words in tweets on Climate Change",
       y = "Sentiment",
       x = NULL) +
  theme(axis.text = element_text(size = 14, color = "black"), 
        axis.title = element_text(size = 14, color = "black"),
        title = element_text(size = 10))

#

```



## find the user tweeting about eu environment

```{r echo=FALSE}
user_eu_environment <-twitter_search_global$euenvironment %>% 
  group_by(screen_name) %>% 
  arrange(desc(followers_count)) 
 # head(10)

unique(user_eu_environment$screen_name)


```

#produce a plot showing the user profiles

```{r}
twitter_search_global$euenvironment%>% 
  group_by(screen_name) %>% 
  arrange(desc(followers_count)) %>% 
  head(20) %>% 
  ggplot(aes(reorder(screen_name, followers_count), followers_count, fill = name)) + 
  geom_col() + 
  coord_flip() +
  labs(title='Top Users with # On Their Profile', 
       x="Users", 
       caption = "Source: Data collected from Twitter's REST API via rtweet") 
```

#Top tweet by amount of likes

```{r echo=FALSE}
user_eu_environment <-twitter_search_global$euenvironment %>% 
  group_by(text) %>% 
  arrange(desc(favorite_count))%>%
  head(10)

unique(user_eu_environment$text)


```

# Finf the top location where Eu environment is coming from
#Let's transform them in NAs and then remove them with na.omit()

```{r}
twitter_search_global_eu_environment$location[twitter_search_global_eu_environment$location==""] <- NA

#Let's check the names of the top locations
twitter_search_global_eu_environment %>%
  count(location, sort = TRUE) %>%
  mutate(location = reorder(location,n)) %>%
  na.omit() %>%
  head(10)
```

# We can use the function recode form the dplyr package 

```{r}
# We can use the function recode form the dplyr package 
eu_environment_location <- twitter_search_global_eu_environment %>% mutate(location_rec = 
                             recode(location, "London, England" = "United Kingdom", "London, UK" = "United Kingdom",
                                    "Berlin, Deutschland" = "Germany" , "London" = "United Kingdom" , "UK" = "United Kingdom",
                                    "Brussels" = "Belgium" , "Germany" = "Germany" ,
                                    "Brussels, Belgium" = "Belgium", "Berlin" = "Germany" , 
                                    "France" = "France" , "Berlin, Germany" = "Germany" , 
                                    "Paris, France" = "France", "Europa" = "Europe", 
                             ))

# check the names of the top locations 

eu_environment_location %>%
  count(location_rec, sort = TRUE) %>%
  mutate(location_rec = reorder(location_rec,n)) %>%
  na.omit() %>%
  head(20) 

```

# plot top locations

```{r}

eu_environment_location %>%
  count(location_rec, sort = TRUE) %>%
  mutate(location_rec = reorder(location_rec,n)) %>%
  na.omit() %>%
  head(10) %>%
  ggplot(aes(x = location_rec,y = n)) +
  geom_col(fill = "blue") +
  coord_flip() +
  labs(x = "Top Locations",
       y = "Frequency",
       title = "Where Twitter users using europe environment are from") + 
  theme(axis.text = element_text(size = 16, color = "black"), 
        axis.title = element_text(size = 16, color = "black"),
        title = element_text(size = 10))

```

# get image url from twitter

```{r}
eu_environment_image_url <- twitter_search_global_eu_environment %>%
  filter(!is.na(media_url)) %>% 
  select(media_url) %>% 
  head(5)

eu_environment_image_url$media_url
```

#Now displaying the images gotten from eu_environment
# Eu enviornment image 1
```{r fig.height=8, fig.width=8}
eu_environment_Image1 <- ("http://pbs.twimg.com/media/EfNvn8pXsAImjXw.jpg")
eu_environment_Image1b <- image_read(eu_environment_Image1)
plot(eu_environment_Image1b)

```

#Eu environment image 2

```{r fig.height=8, fig.width=10}
eu_environment_Image2 <- ("http://pbs.twimg.com/media/EfC5vcNX0AEGGb6.jpg")
eu_environment_Image2b <- image_read(eu_environment_Image2)
plot(eu_environment_Image2b)

```


# Now let's focus on search word Eu Biodiversity

# Find the popular words from the tweets 

```{r}
twitter_search_global_eu_biodiversity <- twitter_search_global$eubiodiversity
twitter_search_global_eu_biodiversity

head(twitter_search_global_eu_biodiversity$text)

# Frist, remove http elements manually
twitter_search_global_eu_biodiversity$stripped_text <- gsub("http.*","",  twitter_search_global_eu_biodiversity$text)
twitter_search_global_eu_biodiversity$stripped_text <- gsub("https.*","", twitter_search_global_eu_biodiversity$stripped_text)
head(twitter_search_global_eu_biodiversity$stripped_text)

# Let's remove punctuation, convert to lowercase, add id for each tweet:
twitter_search_global_eu_biodiversity_clean <- twitter_search_global_eu_biodiversity %>%
  select(stripped_text) %>% 
  mutate(tweetnumber = row_number()) %>% # create new variable denoting the tweet number
  unnest_tokens(word, stripped_text)

head(twitter_search_global_eu_biodiversity_clean)

# Now you can plot your data. 
# plot the top 10 words -- notice any issues?
twitter_search_global_eu_biodiversity_clean %>%
  count(word, sort = TRUE) %>% # count of number of occurencies of each word and sort according to count
  head(10) %>% # extract top 10 words
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "pink", color = "red") +
  coord_flip() +
  labs(x = "Unique Words",
       y = "Frequency",
       title = "Count of unique words found in tweets with #climatechange") + 
  theme(axis.text = element_text(size = 16, color = "black"), 
        axis.title = element_text(size = 16, color = "black"),
        title = element_text(size = 18))

# load list of stop words - from the tidytext package
data("stop_words")
#
# view first 6 words
head(stop_words)
# the lexicon is the source of the stop word.
#
nrow(twitter_search_global_eu_biodiversity_clean)
#

# remove stop words from your list of words
eu_biodiversity_cleaned_tweet_words <- twitter_search_global_eu_biodiversity_clean %>%
  anti_join(stop_words) # return all rows from climate_tweets_clean where there are not matching values in stop_words
#
# there should be fewer words now
nrow(eu_biodiversity_cleaned_tweet_words)

eu_biodiversity_cleaned_tweet_words %>%
  count(word, sort = TRUE) %>%
  head(10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "pink", color = "red") +
  coord_flip() +
  labs(x = "Unique Words",
       y = "Frequency",
       title = "Top 10 most popular words found in tweets with #eu biodiversity") + 
  theme(axis.text = element_text(size = 14, color = "black"), 
        axis.title = element_text(size = 14, color = "black"),
        title = element_text(size = 16))

# Define our own stopwords that we don't want to include 
eu_biodiversity_words <- data.frame(word = c("eubiodiversity", "eu", "biodiversity" , "europe"))

# remove our own stopwords from the list of words too
eu_biodiversity_cleaned_tweet_words_2 <- eu_biodiversity_cleaned_tweet_words %>%
  anti_join(eu_biodiversity_words) 
#
# there should be fewer words now
nrow(eu_biodiversity_cleaned_tweet_words_2)

# plot the top 10 most popular words found in tweets with #climatechange
eu_biodiversity_cleaned_tweet_words_2 %>%
  count(word, sort = TRUE) %>%
  head(10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "pink", color = "red") +
  coord_flip() +
  labs(x = "Unique Words",
       y = "Frequency",
       title = "Top 10 most popular words found in tweets with #climatechange") + 
  theme(axis.text = element_text(size = 14, color = "black"), 
        axis.title = element_text(size = 14, color = "black"),
        title = element_text(size = 16))


```

### plot Wordclouds for eu biodiversity

```{r}
head(eu_biodiversity_cleaned_tweet_words_2)

# the count of each word / the total count
#
eu_biodiversity_cleaned_tweet_words_3 <- eu_biodiversity_cleaned_tweet_words_2 %>%
  count(word, sort = TRUE) %>% 
  mutate(freq = n / sum(n))
head(eu_biodiversity_cleaned_tweet_words_3)

# Read the help file of wordcloud so that you can see what the arguments do
#
with(eu_biodiversity_cleaned_tweet_words_3, 
     wordcloud(word, freq, 
               min.freq = 1, 
               max.words = 50,
               random.order = FALSE, 
               colors = brewer.pal(8, "Dark2"), 
               scale = c(4.5, 0.1)))

title(main = "Wordcloud for Tweets containing #eubiodiversity", 
      cex.main = 2) # Controls the size of the title

display.brewer.all()

eu_biodiversity_cleaned_tweet_words_4 <- eu_biodiversity_cleaned_tweet_words_3 %>% select(word, freq)
#
# Produce wordcloud
#
wordcloud2(eu_biodiversity_cleaned_tweet_words_4)


```

#positive abd negative words

```{r}
# Join sentiment classification to the tweet words
eu_biodiversity_bing_word_counts <- eu_biodiversity_cleaned_tweet_words_2 %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  mutate(word = reorder(word, n)) 
head(eu_biodiversity_bing_word_counts)
#
#
# Finally, plot top words, grouped by positive vs. negative sentiment. 
# it could be interesting to plot sentiment over time to see how sentiment changed over time.
#
eu_biodiversity_bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(title = "Most common Positive and Negative words in tweets on eu biodiversity",
       y = "Sentiment",
       x = NULL) +
  theme(axis.text = element_text(size = 14, color = "black"), 
        axis.title = element_text(size = 14, color = "black"),
        title = element_text(size = 10))

#

```



## find the user tweeting about eu biodiversity

```{r echo=FALSE}
user_eu_biodiversity <-twitter_search_global$eubiodiversity %>% 
  group_by(screen_name) %>% 
  arrange(desc(followers_count)) 
 # head(10)

unique(user_eu_biodiversity$screen_name)


```

#produce a plot showing the user profiles

```{r}
twitter_search_global$eubiodiversity%>% 
  group_by(screen_name) %>% 
  arrange(desc(followers_count)) %>% 
  head(20) %>% 
  ggplot(aes(reorder(screen_name, followers_count), followers_count, fill = name)) + 
  geom_col() + 
  coord_flip() +
  labs(title='Top Users with # On Their Profile', 
       x="Users", 
       caption = "Source: Data collected from Twitter's REST API via rtweet") 
```

#Top tweet by amount of likes

```{r echo=FALSE}
user_eu_biodiversity <-twitter_search_global$eubiodiversity %>% 
  group_by(text) %>% 
  arrange(desc(favorite_count))%>%
  head(10)

unique(user_eu_biodiversity$text)


```

# Finf the top location where Eu environment is coming from
#Let's transform them in NAs and then remove them with na.omit()

```{r}
twitter_search_global_eu_biodiversity$location[twitter_search_global_eu_biodiversity$location==""] <- NA

#Let's check the names of the top locations
twitter_search_global_eu_biodiversity %>%
  count(location, sort = TRUE) %>%
  mutate(location = reorder(location,n)) %>%
  na.omit() %>%
  head(10)
```

# We can use the function recode form the dplyr package 

```{r}
# We can use the function recode form the dplyr package 
eu_biodiversity_location <- twitter_search_global_eu_biodiversity %>% mutate(location_rec = 
                             recode(location, "London, England" = "United Kingdom", "London, UK" = "United Kingdom",
                                    "Berlin, Deutschland" = "Germany" , "London" = "United Kingdom" , "UK" = "United Kingdom",
                                    "Brussels" = "Belgium" , "Germany" = "Germany" , "European Union" = "Europe" , 
                                    "European Union " = "Europe" ,  "12-14 Lr Mount St, Dublin 2" = "Ireland" ,
                                    "Brussels, Belgium" = "Belgium", "Berlin" = "Germany" ,  
                                    "Stockholm, Sweden" = "Sweden", "Uppsala, Sverige" = "Sweden" , 
                                    "France" = "France" , "Berlin, Germany" = "Germany" , 
                                    "Paris, France" = "France", "Europa" = "Europe", 
                             ))

# check the names of the top locations 

eu_biodiversity_location %>%
  count(location_rec, sort = TRUE) %>%
  mutate(location_rec = reorder(location_rec,n)) %>%
  na.omit() %>%
  head(20) 

```

# plot top locations

```{r}

eu_biodiversity_location %>%
  count(location_rec, sort = TRUE) %>%
  mutate(location_rec = reorder(location_rec,n)) %>%
  na.omit() %>%
  head(10) %>%
  ggplot(aes(x = location_rec,y = n)) +
  geom_col(fill = "blue") +
  coord_flip() +
  labs(x = "Top Locations",
       y = "Frequency",
       title = "Where Twitter users using europe environment are from") + 
  theme(axis.text = element_text(size = 16, color = "black"), 
        axis.title = element_text(size = 16, color = "black"),
        title = element_text(size = 10))

```

# get image url from twitter

```{r}
eu_biodiversity_image_url <- twitter_search_global_eu_biodiversity %>%
  filter(!is.na(media_url)) %>% 
  select(media_url) %>% 
  head(5)

eu_biodiversity_image_url$media_url
```

#Now displaying the images gotten from eu_biodiversity
# Eu enviornment image 1
```{r fig.height=8, fig.width=8}
eu_biodiversity_Image1 <- ("http://pbs.twimg.com/media/EfR1ds8XkAEJQvc.jpg")
eu_biodiversity_Image1b <- image_read(eu_biodiversity_Image1)
plot(eu_biodiversity_Image1b)

```

#Eu environment image 2

```{r fig.height=8, fig.width=10}
eu_biodiversity_Image2 <- ("https://pbs.twimg.com/media/EfOBxdMWAAAd4NI?format=jpg&name=900x900")
eu_biodiversity_Image2b <- image_read(eu_biodiversity_Image2)
plot(eu_biodiversity_Image2b)

```

```{r}
cultural_ecosystem <- search_tweets(
  q = "cultural ecosystem", n = 1000
)
cultural_ecosystem 
```


```{r fig.height=5, fig.width=10}

head(cultural_ecosystem$text)

# Frist, remove http elements manually
cultural_ecosystem$stripped_text <- gsub("http.*","",  cultural_ecosystem$text)
cultural_ecosystem$stripped_text <- gsub("https.*","", cultural_ecosystem$stripped_text)
head(cultural_ecosystem$stripped_text)

# Let's remove punctuation, convert to lowercase, add id for each tweet:
cultural_ecosystem_clean <- cultural_ecosystem %>%
  select(stripped_text) %>% 
  mutate(tweetnumber = row_number()) %>% # create new variable denoting the tweet number
  unnest_tokens(word, stripped_text)

head(cultural_ecosystem_clean)

# Now you can plot your data. 
# plot the top 10 words -- notice any issues?
cultural_ecosystem_clean %>%
  count(word, sort = TRUE) %>% # count of number of occurencies of each word and sort according to count
  head(10) %>% # extract top 10 words
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "pink", color = "red") +
  coord_flip() +
  labs(x = "Unique Words",
       y = "Frequency",
       title = "Count of unique words found in tweets with #cultural_ecosystem") + 
  theme(axis.text = element_text(size = 16, color = "black"), 
        axis.title = element_text(size = 16, color = "black"),
        title = element_text(size = 18))

# load list of stop words - from the tidytext package
data("stop_words")
#
# view first 6 words
head(stop_words)
# the lexicon is the source of the stop word.
#
nrow(cultural_ecosystem_clean)
#

# remove stop words from your list of words
cultural_ecosystem_cleaned_tweet_words <- cultural_ecosystem_clean %>%
  anti_join(stop_words) # return all rows from climate_tweets_clean where there are not matching values in stop_words
#
# there should be fewer words now
nrow(cultural_ecosystem_cleaned_tweet_words)

cultural_ecosystem_cleaned_tweet_words %>%
  count(word, sort = TRUE) %>%
  head(10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "pink", color = "red") +
  coord_flip() +
  labs(x = "Unique Words",
       y = "Frequency",
       title = "Top 10 most popular words found in tweets with #eu biodiversity") + 
  theme(axis.text = element_text(size = 14, color = "black"), 
        axis.title = element_text(size = 14, color = "black"),
        title = element_text(size = 16))

# Define our own stopwords that we don't want to include 
cultural_ecosystem_words <- data.frame(word = c("cultural ecosystem", "culturalecosystem", "cultural" , "ecosystem"))

# remove our own stopwords from the list of words too
cultural_ecosystem_cleaned_tweet_words_2 <- cultural_ecosystem_cleaned_tweet_words %>%
  anti_join(cultural_ecosystem_words) 
#
# there should be fewer words now
nrow(cultural_ecosystem_cleaned_tweet_words_2)

# plot the top 10 most popular words found in tweets with #climatechange
cultural_ecosystem_cleaned_tweet_words_2 %>%
  count(word, sort = TRUE) %>%
  head(10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "pink", color = "red") +
  coord_flip() +
  labs(x = "Unique Words",
       y = "Frequency",
       title = "Top 10 most popular words found in tweets with #cultural_ecosystem") + 
  theme(axis.text = element_text(size = 14, color = "black"), 
        axis.title = element_text(size = 14, color = "black"),
        title = element_text(size = 16))

```






